Tunnels to Towers: Secure Virtual Private Networking for CCN

### 2016-12-31 paper/01-introduction.tex
More text

In ICN (or more specifically, CCN and NDN), ANDaNA was the first anonymity network of its 
kind. Similar to Tor, ANDaNA uses circuits formed from anonymizing routers (ARs)
to marshall requests and responses between consumers and producers. The former
onion-encrypt interests and content using the public key(s) of the target ARs.
A variant of ANDaNA uses symmetric keys for packet encapsulation but suffers from
linkability. Tsudik et al. \cite{ac3n} proposed an optimized version of the symmetric-key
ANDaNA variant that did not permit linkability. To the best of our knowledge, there
is no anonymity network variant for ICN architectures. Though tunneling is only 
useful for only a subset of ICN traffic, we believe it is a gap to be addressed 
for this emerging technology, for a variety of reasons. {\bf First},

XXX: consumer privacy outside an AS is important, e.g., XXX
XXX: 
XXX:

>>>>

In ICN (or more specifically, CCN and NDN), ANDaNA was the first anonymity network of its
kind. Similar to Tor, ANDaNA uses circuits formed from anonymizing routers (ARs)
to marshall requests and responses between consumers and producers. The former
onion-encrypt interests and content using the public key(s) of the target ARs.
A variant of ANDaNA uses symmetric keys for packet encapsulation but suffers from
linkability. Tsudik et al. \cite{ac3n} proposed an optimized version of the symmetric-key
ANDaNA variant that did not permit linkability. To the best of our knowledge, there
is no anonymity network variant for ICN architectures. Though tunneling is only
useful for only a subset of ICN traffic, we believe it is a gap to be addressed
for this emerging technology, for a variety of reasons. {\bf First}, privacy
continues to be an elusive property for CCN applications. Tunneling will help
permit some degree of privacy within trusted AS domains from external passive
eavesdroppers. {\bf Second}, multi-hop circuits as used in ANDaNA are overkill
when trying to retain privacy instead of anonymity. {\bf Third}, end-to-end
sessions such as those enabled by CCNxKE \cite{ccnxke} and similar protocols
only serve those engaged in the session. In contrast, since the threat model is
different, tunneled traffic has the potential to serve any number of consumers
within the same trusted domain. Thus, while tunneling may contrast the content-centric
nature of data transmission in CCN, it fills a needed void for this architecture.

In this paper, we present CCVPN, a secure tunneling protocol and system design for
CCN. Similar to ANDaNA, CCVPN encrypts interests and content objects between producers
and consumers. In contrast, CCVPN only encrypts packets between a \emph{single}
source and destination to form a tunnel. In the standard configuration, both
endpoints of the tunnel are gateways between two trusted domains. It is possible,
however, for the source to be an individual consumer. In fact, the standard two-hope
ANDaNA circuit is identical to a nested tunnel with the same source. In this way,
CCVPN is more flexible than a general anonymity network.

XXX
